Computational tools for representation theory of affine Lie algebras

### 2009-07-11 AffineLieAlgebras/ACMS2009/notes.tex
More work on conformal embeddings

\subsubsection{Conformal embeddings}
\label{sec:conformal-embeddings}

\section{Affine Lie algebras representations}
\label{sec:affine-lie-algebras}

>>>>

\subsubsection{Conformal embeddings}
\label{sec:conformal-embeddings}
Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory. !!! Provide an explanation !!!

The states for the theory that corresponds to the algebra $\mathfrak{g}$
\begin{equation}
  \label{eq:109}
  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
\end{equation}
For sub-algebra $\mathfrak{p}\subset\mathfrak{g}$
\begin{equation}
  \label{eq:110}
  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
\end{equation}
Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{p}$ and $\mathcal{P}$ is the projection of $\mathfrak{g}$ to $\mathfrak{p}$. $\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{p}$-invariance, but it is not the case for energy-momentum tensor. So energy-momentum tensor of bigger theory should consist only of generators of $\hat{\mathfrak{p}}$. Then $T_{\hat{\mathfrak{g}}}=T_{\hat{\mathfrak{p}}}\Rightarrow c(\hat{\mathfrak{g}})=c(\hat{\mathfrak{p}})$. This leads to equation
\begin{equation}
  \label{eq:111}
  \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
\end{equation}
Here $x_e$ is the embedding index and $g$, $p$ are dual Coxeter numbers of corresponding algebras. !!! Prove and expand !!!

It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$. 
\section{Affine Lie algebras representations}
\label{sec:affine-lie-algebras}
